Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-13 overview.tex
a few more changes from alexei

%\begin{eqnarray} 
%\frac{\partial \rho}{\partial t} 
%          + \vecv \cdot \grad \rho
%    & = & - \rho \div \vecv,
%        \label{eq:mass} \\
%%
%\frac{\partial \vecv }{ \partial t} 
%          + ( \vecv \cdot \grad ) \vecv 
%    & = & - \frac{1}{\rho} \grad p
%          - \grad \phi,
%        \label{eq:momentum} \\
%%
% \frac{\partial E}{\partial t} + \vecv \cdot \grad E
%    & = & - \frac{1}{\rho} \div (p \vecv) 
%          - \vecv \cdot \grad \phi
%%\nonumber          \\  & &     % uncomment for 2-column
%     + \Gamma - \Lambda
%        \label{eq:total_energy}
%\end{eqnarray}
%
In these equations, $E$, $\rho$, $\vecv$, and $\vecB$ are the comoving
total fluid energy density, comoving gas density, peculiar
velocity, and comoving magnetic field strength, respectively.
$\myvec{I}$ is the identity matrix, and $a$ is the cosmological
expansion parameter (discussed in more detail below).  The first
equation represents conservation of mass, the second conservation of
momentum, and the third conservation of total (kinetic plus thermal)
fluid energy.  They are respectively, the first, second, and third
moments of the Boltzmann equation.  The fourth equation is the
magnetic induction equation.  Terms representing radiative cooling
($\Lambda$) and heating ($\Gamma$) enter on the right-hand side of the
energy equation (\ref{eq:total_energy}), as does the flux due to
thermal heat conduction ($\fcond$).

>>>>

%\begin{eqnarray} 
%\frac{\partial \rho}{\partial t} 
%          + \vecv \cdot \grad \rho
%    & = & - \rho \div \vecv,
%        \label{eq:mass} \\
%%
%\frac{\partial \vecv }{ \partial t} 
%          + ( \vecv \cdot \grad ) \vecv 
%    & = & - \frac{1}{\rho} \grad p
%          - \grad \phi,
%        \label{eq:momentum} \\
%%
% \frac{\partial E}{\partial t} + \vecv \cdot \grad E
%    & = & - \frac{1}{\rho} \div (p \vecv) 
%          - \vecv \cdot \grad \phi
%%\nonumber          \\  & &     % uncomment for 2-column
%     + \Gamma - \Lambda
%        \label{eq:total_energy}
%\end{eqnarray}
%
In these equations, $E$, $\rho$, $\vecv$, and $\vecB$ are the comoving
total fluid energy density, comoving gas density, peculiar
velocity, and comoving magnetic field strength, respectively.
$\myvec{I}$ is the identity matrix, and $a$ is the cosmological
expansion parameter (discussed in more detail below).  The first
equation represents conservation of mass, the second conservation of
momentum, and the third conservation of total (kinetic plus thermal
plus magnetic)
fluid energy.  They are respectively, the first, second, and third
moments of the Boltzmann equation.  The fourth equation is the
magnetic induction equation.  Terms representing radiative cooling
($\Lambda$) and heating ($\Gamma$) enter on the right-hand side of the
energy equation (\ref{eq:total_energy}), as does the flux due to
thermal heat conduction ($\fcond$).

### 2013-06-13 parallel.tex
Minor updates to the AMR section.  Moving ghost zone figure to this section.
a few more changes from alexei

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/amr_hierarchy.eps}
\end{center}
\caption{\emph{Left:} Example of a simple, distributed AMR hierarchy
showing real and ghost grids.  \emph{Right:} Example 2D \enzo\ grid
showing real and ghost zones, as needed for the PPM hydro stencil. }
\label{fig.amr_hierarchy}
\end{figure}

@@

It is advantageous to use \enzo\ in its ``unigrid'' (i.e.,
non-adaptive mesh) mode for a variety of problems, including
non-gravitating turbulence
\citep[e.g.,][]{2002ApJ...569L.127K,Kritsuk04}, the Lyman-$\alpha$ forest
\citep{2005MNRAS.361...70J,2009MNRAS.399.1934P}, or feedback of
metal-enriched gas from galaxies into the intergalactic medium
\citep{2004ApJ...601L.115N,2011ApJ...731....6S}.  Achieving good
scaling of the code in unigrid mode is relatively straightforward --
upon initialization, unigrid simulations are decomposed such that each
MPI process has a roughly equal subvolume (and thus an equal number of grid
cells), meaning that work is evenly distributed.  Communication
patterns for both the gravity solve (which uses a fast Fourier
transform) and the fluid solves (which transfer boundary information
between subvolumes) are predictable and straightforward, and
rebuilding of the grid hierarchy does not take place, removing a
substantial global operation and a great deal of communication.

>>>>

@@

It is advantageous to use \enzo\ in its ``unigrid'' (i.e.,
non-adaptive mesh) mode for a variety of problems, including
non-gravitating turbulence
\citep[e.g.,][]{2002ApJ...569L.127K,Kritsuk04, 2007ApJ...665..416K,
2009ASPC..406...15K}, the Lyman-$\alpha$ forest
\citep{2005MNRAS.361...70J,2009MNRAS.399.1934P}, or feedback of
metal-enriched gas from galaxies into the intergalactic medium
\citep{2004ApJ...601L.115N,2011ApJ...731....6S}.  Achieving good
scaling of the code in unigrid mode is relatively straightforward --
upon initialization, unigrid simulations are decomposed such that each
MPI process has a roughly equal subvolume (and thus an equal number of grid
cells), meaning that work is evenly distributed.  Communication
patterns for both the gravity solve (which uses a fast Fourier
transform) and the fluid solves (which transfer boundary information
between subvolumes) are predictable and straightforward, and
rebuilding of the grid hierarchy does not take place, removing a
substantial global operation and a great deal of communication.
